% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper,uplatex]{article}

\usepackage{hyperref}
\usepackage{geometry}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

% Set your name here
\def\name{Taichi KIMURA}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{http://jblevins.org/projects/cv-template/}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {economics, statistics, mathematics},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=1.25in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

\usepackage{url}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
{\LARGE \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.25in}

\begin{minipage}{0.45\linewidth}
  \#26 Kyousei--Kan \\
  4-1-1, Hiyoshi, Kohoku-Ku, Yokohama \\
  Kanagawa, 223-8526, JAPAN
\end{minipage}
\begin{minipage}{0.45\linewidth}
  \begin{tabular}{ll}
    TEL: & (+81)45-564-2478 \\
    Email: & \href{mailto:tkimura@kbs.keio.ac.jp}{\tt tkimura@kbs.keio.ac.jp}\\
    Web site: & \url{https://ticmrk.github.io/}
  \end{tabular}
\end{minipage}

\section*{Employment}

\begin{itemize}
    \item Assistant professor (Tenured), Graduate School of Business Administration, Keio University, October 2021 - present.
     \item Assistant professor (Non-tenured), Graduate School of Business Administration, Keio University, April 2018 - September 2021.
     \item Research Associate (Non-tenured), Graduate School of Business Administration, Keio University, April 2016 - March 2018.
\end{itemize}

\section*{Education}

\begin{itemize}
  \item Ph.D. Commerce and Management, Hitotsubashi University, March 2016.
  \item M. Commerce, Hitotsubashi University, March 2013.
  \item B. Commerce, Hitotsubashi University, March 2011.
\end{itemize}

\section*{Research interests}

\begin{itemize}
  \item Management Accounting
  \item Management Control
  \item Performance Evaluation
\end{itemize}

\section*{Working papers}

\begin{itemize}
    \item Designing calibration committees: Size, standards, and rater bias (with Takahiro Morimitsu)
        \begin{itemize}
            \item Available at SSRN: \url{https://ssrn.com/abstract=5443702}
        \end{itemize}

    \item  The role of loss aversion in multi-rater subjective performance evaluations (with Takahiro Morimitsu).
        \begin{itemize}
            \item Under Review at \textit{Management Accounting Research}
            \item Available at SSRN: \url{https://ssrn.com/abstract=5083726}.
        \end{itemize}
    
    \item On the use of calibration committees in subjective performance evaluation (with Takahiro Morimitsu).
        \begin{itemize}
            \item Revise \& Resubmit at \textit{Accounting and Business Research}
            \item Available at SSRN: \url{https://ssrn.com/abstract=4290250}.
        \end{itemize}
    
    \item Conformity pressure and compensation contracts (with Yutaro Murakami). 
        \begin{itemize}
            \item Available at SSRN: \url{https://ssrn.com/abstract=4113994}.
        \end{itemize}
\end{itemize}

\section*{Research}

\subsection*{Refereed Research Article}

\begin{itemize}
    \item Cost--based pricing in government procurement with unobservable cost-reducing actions and productivity (with Takahiro Morimitsu), 2023, \textit{Asia--Pacific Journal of Accounting and Economics}, 30(2): 373-390.
    
    \item The impact of the communication and the use of performance evaluation information on the organizational identification, 2019, \textit{Keio Business Forum} 36(1): 39--56. (in Japanese)

	\item Application of a formative scale development guideline to management accounting researches (with Yoshitaka Shirinashihama, Liu Meiling, and Yuichi Ichihara), 2017, \textit{Hitotsubashi Review of Commerce and Management}12(2): 62--71. (in Japanese)

	\item Organizational culture concept in management accounting research: Past, present and future, 2014, \textit{The Journal of Cost Accounting Research} 30(2): 52-64. (in Japanese)
\end{itemize}

\subsection*{Non-refereed Article}

\begin{itemize}
    \item Impacts of peer pressure on incentive design: A review of analytical research (with Yutaro Murakami), 2022, \textit{Financial and Cost Accounting (Sangyo Keiri)} 82(2): 111--124. (in Japanese)

    \item Biases in subjective performance evaluation: A review of analytical research (with Takahiro Morimitsu), 2021, \textit{The Commercial Review of Seinan Gakuin University} 68(1-2): 65--88. (in Japanese)
    
	\item The use of formative indicators in management accounting research: A note on measurement model specification (with Liu Meilling, Yuichi Ichihara, and Yoshitaka Shirinashihama), 2015, \textit{Melco Journal of Management Accounting Research} 8(1): 77-87. (in Japanese)

	\item A review of empirical management accounting research using the concept of organizational culture: Focusing on the view of organizational culture, 2015, \textit{Kigyo Kaikei} 67(8): 1179-1185. (in Japanese)
\end{itemize}

\subsection*{Book}

\begin{itemize}
    \item \textit{Business Accounting <5th ed.>}, 2024, ChuoKeizai-Sha Inc.: Tokyo. (with Takashi Yamane, Yasuhiro Ohta, and Yutaro Murakami, in Japanese)
\end{itemize}

\subsection*{Book Chapter}

\begin{itemize}
	\item Career concern in non-profit organizations, 2021, in Yasuhiro Ohta ed. \textit{Accounting for Personnel Evaluation}, ChuoKeizai-Sha Inc.: Tokyo, Chapter 4, pp.63--81. (in Japanese)
\end{itemize}


\subsection*{Other Publications}

\begin{itemize}
	\item Government procurement contract design for encouraging cost reduction (with Takahiro Morimitsu), 2017, \textit{Proceedings of 29th Asian--Pacific Conference on International Accounting Issue}.
\end{itemize}

\section*{Presentations}
\subsection*{Conference Presentations}

\begin{itemize}
    \item 47th Annual Congress of European Accounting Association (Rome, Italy), May 2025, ``The role of loss aversion in multi-rater subjective performance evaluations'' (with Takahiro Morimitsu).
    \item 33rd Asian-Pacific Conference on International Accounting Issues (Vancouver, Canada), November 2024, ``The role of loss aversion in multi-rater subjective performance evaluations'' (with Takahiro Morimitsu).
    \item 83rd Japan Accounting Association Annual Meeting (Waseda University, Japan), August 2024, ``A calibration committee with a loss-averse agent'' (with Takahiro Morimitsu).
    \item 32nd Asian-Pacific Conference on International Accounting Issues (Gold Coast, Australia), October 2023, ``On the use of calibration committees in subjective performance evaluation'' (with Takahiro Morimitsu).
    \item 45th Annual Congress of European Accounting Association (Helsinki-Espoo, Finland), May 2023, ``On the use of calibration committees in subjective performance evaluation'' (with Takahiro Morimitsu).
    \item 81st Japan Accounting Association Annual Meeting (The University of Tokyo (online), Japan), August 2022, ``Showing off in subjective performance evaluation'' (with Takahiro Morimitsu).
    \item 2022 The Japanese Association of Management Accounting Annual Meeting (Meiji University, Japan), August 2022, ``Showing off in subjective performance evaluation''  (with Takahiro Morimitsu).
    \item 79th Japan Accounting Association Annual Meeting (Hokkaido University (online), Japan), September 2020, ``Cost--based pricing in government procurement with unobservable cost-reducing actions and productivity'' (with Takahiro Morimitsu).
    \item 31st Asian--Pacific Conference on International Accounting Issue (Warsaw, Poland), October 2019, ``Conformity Pressure and Compensation Contracts'' (with Yutaro Murakami).
    \item 78th Japan Accounting Association Annual Meeting (Kobe Gakuin University, Japan), September 2019, `Cost--based pricing in government procurement with unobservable cost-reducing actions and productivity'' (with Takahiro Morimitsu).
    \item 42nd Annual Congress of European Accounting Association (Paphos, Cyprus), May 2019, '`Conformity Pressure and Compensation Contracts'' (with Yutaro Murakami).
    \item 30th Asian--Pacific Conference on International Accounting Issue (San Francisco, USA), November 2018, ``Disagreement and performance evaluation systems.''
    \item 77th Japan Accounting Association Annual Meeting (Kanagawa University, Japan), September 2018, ``Disagreement and performance evaluation systems.''
    \item 29th Asian--Pacific Conference on International Accounting Issue (Kuala Lumpur, Malaysia), November 2017, ``Government procurement contract design for encouraging cost reduction'' (with Takahiro Morimitsu)
    \item 76th Japan Accounting Association Annual Meeting (Hiroshima University, Japan), September 2017, ``Government procurement contract design for encouraging cost reduction'' (with Takahiro Morimitsu).
    \item 2016 Japan Cost Accounting Association Kanto Meeting (Ishinomaki Senshu University, Japan), February 2017, ``Government procurement contract design for encouraging cost reduction'' (with Takahiro Morimitsu).
    \item 41st Japan Cost Accounting Association Annual Meeting (Nihon University, Japan), September 2015, ``A Quantitative study on the effects of performance indicator communication: The mediating role of organizational identification.''
    \item 39th Japan Cost Accounting Association Annual Meeting (Senshu University, Japan), September 2013, ``The concept of organizational culture in management accounting research: A literature review.''
\end{itemize}

\subsection*{Invited Seminars and Workshops (from 2023)}

\begin{itemize}
    \item 98th Analytical Accounting Research Workshop (Yokohama, Japan), November 2025, ``Designing calibration committees: Size, standards, and rater bias.''
    \item Contract Theory Workshop (Osaka, Japan), November 2025, ``Designing calibration committees: Size, standards, and rater bias.''
    \item 18th Applied Economics and Management Workshop (Niigata, Japan), March 2025, ``The role of loss aversion in multi-rater subjective performance evaluations.''
    \item 67th Handai Accounting Research Seminar (Osaka, Japan), November 2024, ``The role of loss aversion in multi-rater subjective performance evaluations.''
    \item 97th Analytical Accounting Research Workshop (Kyoto, Japan), August 2024, ``A calibration committee with a loss-averse agent.''
    \item 60th Doshisha Experimental Accounting and Finance Research (Online), May 2023, ``On the use of calibration committees in subjective performance evaluation.''
    \item 94th Analytical Accounting Research Workshop (Fukuoka, Japan), March 2023, ``On the use of calibration committees in subjective performance evaluation.''
\end{itemize}

\section*{Teaching}

\subsection*{Teaching experiences}

\begin{itemize}
	\item Accounting and Control (MBA Core), Keio University, 2016--present.
	\item Accounting and Control (EMBA Core), Keio University, 2018--present.
	\item Management Accounting (MBA Elective), Keio University, 2018--present.
\end{itemize}

\subsection*{Cases and teaching materials}

\begin{itemize}
    \item Next Step Japan Inc., 2025, Keio Business School Case. (in Japanese)
    \item Planet Golf, 2023, Keio Business School Case. (in Japanese)
    \item Introduction to Management Accounting, 2021, Keio Business School Case. (in Japanese)
    \item Tsunashima Metal Inc., 2021, Keio Business School Case. (in Japanese)
    \item Kozukue Tire Inc., 2021, Keio Business School Case. (in Japanese)
    \item Introduction to Cost Accounting, 2020 (Rev.2024), Keio Business School Case. (in Japanese)
    \item Mitsubishi Electric Corporation (with Takahiro Morimitsu), 2018, Keio Business School Case. (in Japanese)
    \item Amoeba Management under JAL's Reconstruction, 2016 (Rev. 2023), Keio Business School Case. (in Japanese)
\end{itemize}

\section*{Grants}

\begin{itemize}
\item Theoretical Study on the Mechanisms of Bias in Subjective Performance Evaluations and Their Mitigation Strategies (4,290,000JPY, PI), Grant Number 24K05206, April 2024 -- March 2027.

\item An Analysis of Goal Setting and Non--linear Incentive Schemes, JSPS Kakenhi Grant-in-Aid for Early-Career Scientists (4,160,000JPY, PI), Grant Number 21K13406, April 2021 -- March 2024.

\item Reconsideration of Management Control Theory from the Viewpoint of Behavioral Contract Theory, JSPS Kakenhi Grant-in-Aid for Early-Career Scientists (3,120,000JPY, PI), Grant Number 18K12897, April 2018 -- March 2021.

\item Heterogeneous Beliefs and Management Control System, JSPS Kakenhi Grant-in-Aid for Research Activity Start-up (1,560,000JPY, PI), Grant Number 16H07173, April 2016 -- March 2018.

\item The Effects of Organizational Identification on Performance Measurement Systems, Grant from The Melco Foundation (391,000JPY, PI), January 2014 -- December 2014.
\end{itemize}

\section*{Membership}

\begin{itemize}
\item Japan Accounting Association
\item The Accounting and Economic Association of Japan
\item Japan Cost Accounting Association
\item The Japanese Association of Management Accounting
\item European Accounting Association
\end{itemize}

\bigskip

% Footer
\begin{center}
  \begin{footnotesize}
    Last updated: \today \\
    %\href{\footerlink}{\texttt{\footerlink}}
  \end{footnotesize}
\end{center}

\end{document}
